Blocking-resistant communication through high-value web services

### 2014-05-13 docs/meek.tex
Stick with the "reflector" terminology.

meek has a home page at
\url{https://trac.torproject.org/projects/tor/wiki/doc/meek}.
Our source code is in the Git repository at
\url{https://git.torproject.org/pluggable-transports/meek.git}.
As of version 0.5 (May~7, 2014), the source code consists of
about 800 lines of Go for the client programs,
400 lines for \meekserver, and
100 lines for the intermediary web app.
Each of the browser extensions
(one for Firefox, one for Chrome)
is about 300 lines of JavaScript.

>>>>

meek has a home page at
\url{https://trac.torproject.org/projects/tor/wiki/doc/meek}.
Our source code is in the Git repository at
\url{https://git.torproject.org/pluggable-transports/meek.git}.
As of version 0.5 (May~7, 2014), the source code consists of
about 800 lines of Go for the client programs,
400 lines for \meekserver, and
100 lines for the reflector web app.
Each of the browser extensions
(one for Firefox, one for Chrome)
is about 300 lines of JavaScript.
